### 2016-04-20 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updates to Hose Stream report

\Flushright{Regarding Non-Metric Units: The policy of the National Institute of Standards and Technology is to
use metric units in all its published materials. To aid the understanding of this report, in most cases,
measurements are reported in both metric and U.S. customary units. There are instances in this study where only the U.S. customary units are used as they relate to specific equipment or common fire service vernacular}

@@

There exists a multitude of different tools, methods, and techniques used to apply water for fire suppression using hose streams. A common type of nozzle that is used to apply water during fire suppression in residential structures is an adjustable-pattern spray nozzle, commonly referred to as a combination nozzle~\cite{NFPA1964}. Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns. The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}. Increasing the angle of the stream allows for a larger area to be covered by the water spray.  However, increasing the angle decreases the distance reached by the stream and its penetration power. 
%\textit{Essentials of Fire Fighting} defines 
%https://docs.google.com/presentation/d/1hZ5DZhYXxCkcIEHNZKumH48b_Q53iM2D7asXkMYlVMM/embed?hl=en&size=l&slide=id.p39

@@

The approximate locations of the bi-directional probes are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}. To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report. The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6", contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway. The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.

@@

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a ``near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near" target (top row) and ``far" target (bottom row) during the monitor experiments in the West Structure.}
	\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17. The stairwell door was opened for the entire test series. The test series began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Then, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated using the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_70_pic} contains images of the straight stream from the combination nozzle and solid stream from the smooth bore nozzle during Test 70.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_70}
	\end{center} 
	\endminipage
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SB_70}
	\end{center}
	\endminipage
	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
	\label{fig:test_70_pic}
\end{figure}
\FloatBarrier

@@

% Where was the handline aimed? Add flow chart? %
Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by using a straight stream to flow water in a fixed,horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping the ceiling, clockwise, and counterclockwise application patterns. This entire procedure was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18 with the flow path fully established.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{5}{c}{\large ------------------------ 120 GPM ------------------------} 
\\
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
\\
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
\\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counterclockwise rotation during Test 18. Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 34}
\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
\\ \multicolumn{7}{c}{} \\
\textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
\\ \multicolumn{7}{c}{} \\
\textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 19}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns.}
	\label{fig:Test_70_BDP_A10_Avg_All}
	\end{figure}
\FloatBarrier

>>>>

\flushright{Regarding Non-Metric Units: The policy of the National Institute of Standards and Technology is to
use metric units in all its published materials. To aid the understanding of this report, in most cases,
measurements are reported in both metric and U.S. customary units. There are instances in this study where only the U.S. customary units are used as they relate to specific equipment or common fire service vernacular}

@@

There exists a multitude of different tools, methods, and techniques used to apply water for fire suppression using hose streams. A common type of nozzle that is used to apply water during fire suppression in residential structures is an adjustable-pattern spray nozzle, commonly referred to as a combination nozzle~\cite{NFPA_1964}. Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns. The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}. Increasing the angle of the stream allows for a larger area to be covered by the water spray.  However, increasing the angle decreases the distance reached by the stream and its penetration power. 
%\textit{Essentials of Fire Fighting} defines 
%https://docs.google.com/presentation/d/1hZ5DZhYXxCkcIEHNZKumH48b_Q53iM2D7asXkMYlVMM/embed?hl=en&size=l&slide=id.p39

@@

The approximate locations of the bi-directional probes are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}. To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report. The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6'', contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway. The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10'', contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.

@@

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a ``near'' target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target, located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during the monitor experiments in the West Structure.}
	\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17. The stairwell door was opened for the entire test series. The test series began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Then, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated using the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_70_pic} contains images of the straight stream from the combination nozzle and solid stream from the smooth bore nozzle during Test 70.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_70}
	\end{center} 
	\endminipage
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SB_70}
	\end{center}
	\endminipage
	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
	\label{fig:test_70_pic}
\end{figure}
\FloatBarrier

@@

% Where was the handline aimed? Add flow chart? %
Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns. This entire procedure was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18 with the flow path fully established.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{5}{c}{\large ------------------------ 120 GPM ------------------------} 
\\
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & 1.0 $\pm0.2$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$ & 2.4 $\pm0.4$
\\ \midrule
 & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
\\
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
\\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.3$ & 1.9 $\pm0.3$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.3$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

% StdDev Values
% \midrule
% \textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
% \\ \multicolumn{6}{c}{} \\
% \textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
% \\ \multicolumn{6}{c}{} \\
% \textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
% \\ \midrule
%  & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
% \\
%  & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
% \\
% \textbf{Stream} &
% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
% \multicolumn{3}{c}{} 
% \\
% \midrule
% \textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
% \\ \multicolumn{6}{c}{} \\
% \textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
% \\
% \bottomrule

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 18. Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 34}
\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
\\ \multicolumn{7}{c}{} \\
\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
\\ \multicolumn{7}{c}{} \\
\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ & 2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

% StdDev values
% \\ \midrule
% \textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
% \\ \multicolumn{7}{c}{} \\
% \textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
% \\ \multicolumn{7}{c}{} \\
% \textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
% \\ \bottomrule

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 19}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}

% StdDev +- values
% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
% \\ \midrule
% \textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
% \\ \multicolumn{5}{c}{} \\
% \textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
% \\ \multicolumn{5}{c}{} \\
% \textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
% \\ \midrule
%  & \multicolumn{4}{c}{\underline{Test 19}}
% \\
% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
% \\ \midrule
% \textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
% \\ \multicolumn{5}{c}{} \\
% \textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
% \\ \multicolumn{5}{c}{} \\
% \textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
% \\ \bottomrule

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns. \textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the 2nd floor, west double door}}
	\label{fig:Test_70_BDP_A10_Avg_All}
	\end{figure}
\FloatBarrier
